An Imaging Search for Circumstellar Companions of Sirius B

### 2021-08-04 paper/paper.tex
update paper

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities and sub-AU separations, reaching $\sim$\qty{3.5}{\jupitermass} at $\sim$\qty{0.25}{\au} down to a sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}. The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the high-precision of the Sirius B system age. We do not detect any companions around Sirius B, consistent with previous studies.
\end{abstract}

@@

There is limited knowledge of planetary systems around evolved stars. \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase. Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}. During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.

@@

The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \cite{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes. We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.

>>>>

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities and sub-AU separations, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au} down to a sensitivity of \qty{0.6}{\jupitermass} at \qty{1.5}{\au}. The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the high-precision of the Sirius B system age. We do not detect any companions around Sirius B, consistent with previous studies.
\end{abstract}

@@

There is limited knowledge of planetary systems around evolved stars. \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase. Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}. During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.

@@

The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes. We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
